The Host Galaxies of Rapidly Evolving Transients in the Dark Energy Survey

### 2020-04-09 RET_Hosts_SNWG.tex
Updates from Overleaf

\begin{figure*}
\includegraphics[width=\textwidth]{mc_figs/rets_s12_param_diffs_ssfr_final.png}
\caption{Histograms showing the differences between the fit parameters across the MCMC samples.
\label{fig:param_diffs}}
\end{figure*}

@@

To compare two distributions we follow the method outlined in \citetalias{Wiseman2020}. We fit the PDFs, along with the uncertainty on the value in each bin, simultaneously with the same priors using the No U-Turn Sampler (NUTS; \citealt{Hoffman2014}) Hamiltonian Monte Carlo algorithm via the  \texttt{pymc3}\footnote{https://docs.pymc.io/} package to explore the posterior distribution. We use a warm-up period of $5\times10^3$ iterations and a fit period of $10^4$ iterations. Fig. \ref{fig:histfit_s12_ssfr} displays an example of the resulting fit where the DES RETs and \citet{Sanders2012} sSFR distributions are compared. Each resulting distribution is described by the `loc' (location), `scale' (spread), and `alpha' (skewness). We then compare the differences in these parameters, as seen in Fig. \ref{fig:param_diffs}, by reporting objectively the percentages of posterior samples that overlap, and subjectively what this means for the similarity of the distributions.
\twocolumn
\begin{figure}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_s13_histfit_ssfr_final.png}
\caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and SNe II, accounting for uncertainties in each bin.
\label{fig:histfit_ssfr_s13}}
\end{figure}
\begin{figure}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_k15_histfit_ssfr_final.png}
\caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and LGRBs, accounting for uncertainties in each bin.
\label{fig:histfit_ssfr_k15}}
\end{figure}
\begin{figure}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_p16_histfit_ssfr_final.png}
\caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and SLSNe, accounting for uncertainties in each bin.
\label{fig:histfit_ssfr_p16}}
\end{figure}

>>>>

\begin{figure*}
\includegraphics[width=\textwidth]{mc_figs/rets_s12_param_diffs_ssfr_final.png}
\caption{Histograms showing the differences between the fit parameters across the MCMC samples for the comparison between RETs and SESNe. 
\label{fig:param_diffs}}
\end{figure*}

@@

To compare two distributions we follow the method outlined in \citetalias{Wiseman2020}. We fit the PDFs, along with the uncertainty on the value in each bin, simultaneously with the same priors using the No U-Turn Sampler (NUTS; \citealt{Hoffman2014}) Hamiltonian Monte Carlo algorithm via the  \texttt{pymc3}\footnote{https://docs.pymc.io/} package to explore the posterior distribution. We utilise two chains, for a warm-up period of $5\times10^3$ iterations per chain and a fit period of $5\times10^3$ iterations per chain. Fig. \ref{fig:histfit_s12_ssfr} displays an example of the resulting fit where the DES RETs and \citet{Sanders2012} sSFR distributions are compared. Each resulting distribution is described by the `loc' (location), `scale' (spread), and `alpha' (skewness). We then compare the differences in these parameters, as seen in Fig. \ref{fig:param_diffs}, by reporting objectively the percentages of posterior samples that overlap, and subjectively what this means for the similarity of the distributions.
\twocolumn
\begin{figure}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_s13_histfit_ssfr_final.png}
\caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and SNe II, accounting for uncertainties in each bin.
\label{fig:histfit_ssfr_s13}}
\end{figure}
\begin{figure}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_k15_histfit_ssfr_final.png}
\caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and LGRBs, accounting for uncertainties in each bin.
\label{fig:histfit_ssfr_k15}}
\end{figure}
\begin{figure}
\includegraphics[width=0.5\textwidth]{mc_figs/rets_p16_histfit_ssfr_final.png}
\caption{Results of the MCMC fits to the PDFs of sSFR for DES RETs and SLSNe, accounting for uncertainties in each bin.
\label{fig:histfit_ssfr_p16}}
\end{figure}
